Avoiding the Global Sort: \break A Faster Contour Tree Algorithm \footnote{The full updated version of this paper is available on the arXiv \cite{rs-mvrms-14}}

### 2015-12-03 paint-contour-tree.tex
labels corrected

\begin{definition}
A \emph{leaf assignment} $\chi$ of a binary tree $T$ assigns \emph{two} distinct leaves to each internal vertex $v$,
one from the left and one from the right subtree of $v$ (or only one leaf if $v$ has only one child). % naturally if $v$ has only one child it is assigned only one color). 
The subroutine $\init(\MM)$ naturally defines a leaf assignment to $\jc(\MM)$ (which 
is a rooted binary tree) according to the priority queue for each up-star we put a given vertex in.  
Call this the \emph{initial coloring} of the vertices in $\jc(\MM)$, and denote it by $\chi$.

@@

\begin{lemma}\label{heapRunTimeBound}
Let $\MM$ be a simplicial complex with $t$ critical points.  
The running time of $\build(\MM)$ is $O(N+t\alpha(t) + \sum_{v \in \jc(\MM)} \log |H_v|)$, where $H_v$ is defined by an initial coloring.
%For every vertex in $\jc(\MM)$, let $H_v$ be defined by the initial coloring of $\MM$.
%The running time of $\build(\MM)$ is $O(N+t\alpha(t) + \sum_{v \in \jc(\MM)} \log |H_v|)$.
\end{lemma}

@@

%\algorithmRunTimeSection
\section{Proof of Lemma~\ref{heapRunTimeBound}}
\label{sec:runTime}
\proofofRunTime

>>>>

\begin{definition}\label{def:initialColoring}
A \emph{leaf assignment} $\chi$ of a binary tree $T$ assigns \emph{two} distinct leaves to each internal vertex $v$,
one from the left and one from the right subtree of $v$ (or only one leaf if $v$ has only one child). % naturally if $v$ has only one child it is assigned only one color). 
The subroutine $\init(\MM)$ naturally defines a leaf assignment to $\jc(\MM)$ (which 
is a rooted binary tree) according to the priority queue for each up-star we put a given vertex in.  
Call this the \emph{initial coloring} of the vertices in $\jc(\MM)$, and denote it by $\chi$.

@@

\begin{lemma}\label{lem:runTimeUpper}
Let $\MM$ be a simplicial complex with $t$ critical points.  
The running time of $\build(\MM)$ is $O(N+t\alpha(t) + \sum_{v \in \jc(\MM)} \log |H_v|)$, where $H_v$ is defined by an initial coloring.
%For every vertex in $\jc(\MM)$, let $H_v$ be defined by the initial coloring of $\MM$.
%The running time of $\build(\MM)$ is $O(N+t\alpha(t) + \sum_{v \in \jc(\MM)} \log |H_v|)$.
\end{lemma}

@@

%\algorithmRunTimeSection
\section{Proof of \Lem{runTimeUpper}}
\label{sec:runTime}
\proofofRunTime
